### 2012-10-29 paper_draft.tex
Added tif-conversions of my svg-plots. Changed in text, doesn't compile?
added wikimedia

Another risk regarding data quality that should be kept in mind is a possible bias in data availability on openSNP: only a subset of people buy DTC genetic testing, from which an even smaller subset is willing to publish the results, which can potentially lead to skewed GWAS-results.

@@

\section*{Figure Legends}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.35]{25_10_2012_Graphs/users.png}
	\end{center}
	\caption{
	{\bf Growth of openSNP-user-accounts.} The increase in numbers for users from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure1_label}
\end{figure}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.35]{25_10_2012_Graphs/genotypes.png}
	\end{center}
	\caption{
	{\bf Growth of available genotypings.} The increase in numbers for genotyping-files from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure2_label}
\end{figure}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.40]{25_10_2012_Graphs/phenotypes_vs_userphenotypes.png}
	\end{center}
	\caption{
	{\bf Development of unique phenotypes and phenotypic information over time.} The x-axis shows the time-frame from start of the project until October 2012, the left y-axis shows how many unique phenotypes have been entered, and the right y-axis shows the amount of phenotypes users entered.}
	\label{pheno}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.5]{25_10_2012_Graphs/papers_dotchart.png}
	\end{center}
	\caption{
	{\bf Distribution of annotation-sources at openSNP.} Currently, SNP-annotations from SNPedia, PLOS, Mendeley, the \emph{GET Evidence System} and the \emph{NHGRI GWAS Catalog} are being collected.}
	\label{Figure3_label}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.1]{25_10_2012_Graphs/percent_oa.png}
	\end{center}
	\caption{
	{\bf Ratio of Open Access Publications.} Green pieces are Open Access. The \emph{NHGRI GWAS Catalog} doesn't give information about the Open Access status.}
	\label{oa_label}
\end{figure}

>>>>

Another risk regarding data quality that should be kept in mind is a possible bias in data availability on openSNP: only a subset of people buy DTC genetic testing, from which an even smaller subset is willing to publish the results, which can potentially lead to skewed GWAS-results. 21 people, mainly from underrepresented demographics, have been offered free genotyping using funding provided by the Wikimedia Germany association in order to mitigate this bias.

@@

\section*{Figure Legends}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.35]{25_10_2012_Graphs/users.tif}
	\end{center}
	\caption{
	{\bf Growth of openSNP-user-accounts.} The increase in numbers for users from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure1_label}
\end{figure}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.35]{25_10_2012_Graphs/genotypes.tif}
	\end{center}
	\caption{
	{\bf Growth of available genotypings.} The increase in numbers for genotyping-files from 27.09.2011 to 27.10.2012 is shown.} 
	\label{Figure2_label}
\end{figure}
\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.40]{25_10_2012_Graphs/phenotypes_vs_userphenotypes.tif}
	\end{center}
	\caption{
	{\bf Development of unique phenotypes and phenotypic information over time.} The x-axis shows the time-frame from start of the project until October 2012, the left y-axis shows how many unique phenotypes have been entered, and the right y-axis shows the amount of phenotypes users entered.}
	\label{pheno}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.5]{25_10_2012_Graphs/papers_dotchart.tif}
	\end{center}
	\caption{
	{\bf Distribution of annotation-sources at openSNP.} Currently, SNP-annotations from SNPedia, PLOS, Mendeley, the \emph{GET Evidence System} and the \emph{NHGRI GWAS Catalog} are being collected.}
	\label{Figure3_label}
\end{figure}

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[scale=0.1]{25_10_2012_Graphs/percent_oa.tif}
	\end{center}
	\caption{
	{\bf Ratio of Open Access Publications.} Green pieces are Open Access. The \emph{NHGRI GWAS Catalog} doesn't give information about the Open Access status.}
	\label{oa_label}
\end{figure}
